Daten nur monatlich:
risk free rate: Bundesstaatsanleihen mit laufzeit einem Monat
futures
CDAX
DAX 
FAZ-Index
TecDax
aus Interesse: SDax (Smallcaps)

\cite{goy17} 
Holding Period 1 3 6 12 36 60, ranking period analogue
overlapping holding periods
INSTEAD TRY TS WITH EXCESS RETURNS!!!!!!!!!!!
CS, TS, CS_TVM, TS_Zero_net_long_investment
scaled unscaled
share code criterion filters out American depository receipts, units, American trust components, closed- end funds, preferred stocks, and real estate investment trusts
sample also excludes micro-cap stocks to avoid potential biases in computed returns, which are particularly severe for low priced stocks (see Blume and Stambaugh 1983 and Lyon, Barber, and Tsai 1999). We, therefore, follow the literature (e.g. Jegadeesh and Titman 1993) and exclude micro-cap stocks. A micro-cap stock is defined as a stock below the 20th percentile of NYSE market capitalization at the end of the ranking period.
For the CS strategy, at each ranking date, we sort stocks into two equal- weighted portfolios based on their prior raw returns in excess of the cross- sectional average. We go long (short) in stocks with returns higher (lower) than the cross-sectional average.
By construction, the CS strategy invests $1 each month on both the long and short sides.
For the TS strategy, we sort stocks based on their prior raw returns in excess of the risk-free rate. We go long (short) in stocks with excess returns bigger (smaller) than zero. 
The long portfolio under the TS strategy is the equal-weighted portfolio of all stocks with positive excess returns during the ranking period and the short portfolio is the equal-weighted portfolio of the other stocks. The long portfolio under the CS strategy is the equal-weighted portfolio of all stocks with returns in excess of cross-sectional mean returns during the ranking period and the short portfolio is the equal-weighted portfolio of the other stocks. We use overlapping portfolios, like in Jegadeesh and Titman (1993), for holding periods greater than 1 month.

They find that the alpha of a well-diversified futures portfolio with a TSMOM strategy yields an impressive excess return of more than 1% per month over the 1985?2009 period.

How to take transaction costs into account? turnover

cite{Jeg93} one month treasury bills as riskfree rate

ZSMh volatility mit risk premiums

\cite{mos12} analyze wether returns are significant for every single contract
relationship btw momentum and sentiment
futures prices for 24 commodities, 12 cross-currency pairs (from nine underlying currencies), nine developed equity indexes, and 13 developed govern- ment bond futures, from January 1965 through December 2009.


SIND TS VLLT MEHR AKTIEN --> MEHR DIVERSIFIKATION???

To ensure that neither bonds futures nor any other single sector drives our findings, we conduct similar analyses for each individual sector, as well as for the overall portfolio excluding one sector at a time kim16
Following Bessembinder (1992), we compute the daily returns as percentage changes using the nearest contracts (until the first trading day of the maturity month), and then roll over to the second- nearest contracts within the delivery month. Monthly returns are calculated by compounding the daily returns. We follow MOP in focusing on a TSMOM strategy with a 12-month lookback period and a one-month holding period, although our tests suggest similar results with other lookback and holding periods. That is, the 12-month returns for 1984 are used to estimate the January 1985 TSMOM profits.
we rank the past 12-month performance of each futures contract into five groups. Following previous studies (e.g., Novy-Marx, 2012), we buy the winners (the top 20%) and sell the losers (the bottom 20%) and hold the portfolio for a month.

which has more effect? short or long?
eine monat pause für serial correlation

value weighting largely alleviates the impact of lead-lag effects on profits.